Demystifying the Computer Science \\PhD Admission in US Universities\\{\large A guide for Vietnamese and International Students

### 2023-06-15 phd-cs-us.tex
Updates from Overleaf

\subsection{Tenured or tenure-track faculty? Who do you choose?} 
The short answer is that tenured-track faculty (e.g., assistant professors) are more likely to be young and very active in research (they have to, in order to get tenure). Thus, they will likely have more time to work with you and push you to do research and publish. The downside is that they may not have as much experience in managing students and may not have as much funding as tenured faculty.
Tenured faculty (e.g., associate and full profs.) are more likely to be older, more well-known, and have more experience in managing students.  However, they might not push you as hard (they don't have to, they already got tenured) and expect you to figure things out yourself (so you need to be very independent).  Some tenured faculty are also no longer active in research, e.g., they are more involved in administrative duties.

@@

\begin{wrapfigure}{l}{0.5\textwidth}
    \vspace{-0.4in}
      \begin{center}
        \includegraphics[width=0.5\textwidth]{c5.png}
      \end{center}
    \vspace{-0.9in}
    \end{wrapfigure}
If you don't know that professor (e.g., first email contact), then use \textbf{Prof. Lastname} or \textbf{Dr. Lastname}. I've seen many international students write \textbf{Prof.} or \textbf{Dr.} \textbf{Firstname Lastname}.  Writing like that makes it like you copy and paste the names, so no need to do so,  just Prof. or Dr. Lastname.

@@

\begin{commentbox}
    Vu: I've been called Dr. Vu and I find it a bit amusing but am totally fine with it.
\end{commentbox}

@@

\subsection{Having fun during a PhD?}
PhD students \emph{and faculty} probably find it amusing about the notion that students, especially international ones, can genuinely enjoy their PhD studies. In fact, after reading posts after posts on VietPhD.org on how PhD students are commonly mistreated, stressed, it seems being miserable is a norm during a PhD study.

There are many advice on surviving PhD that you can follow. But here I just list a few that works for me and what I advice my students to do.\tvn{TODO}

>>>>

\subsection{Tenured or tenure-track faculty? Who do you choose?} 
The short answer is that tenured-track faculty (e.g., assistant professors) are more likely to be young and active in research (they have to, in order to get tenure). Thus, they will likely have more time to work with you and push you to do research and publish. However, they may not have as much experience in managing students and may not have as much funding as tenured faculty.
Tenured faculty (e.g., associate and full profs.) are more likely to be older, more well-known, and have more experience in managing students.  However, they might not push you as hard (they don't have to, they already got tenured) and expect you to figure things out yourself (so you need to be very independent).  Some tenured faculty are also no longer active in research, e.g., they are more involved in administrative duties.

@@

\begin{wrapfigure}{l}{0.5\textwidth}
    \vspace{-0.4in}
      \begin{center}
        \includegraphics[width=0.5\textwidth]{c5.png}
      \end{center}
    \vspace{-0.9in}
    \end{wrapfigure}
If you don't know the professor (e.g., first email contact), then use \textbf{Prof. Lastname} or \textbf{Dr. Lastname}. I've seen many international students write \textbf{Prof.} or \textbf{Dr.} \textbf{Firstname Lastname}.  Writing like that makes it like you copy and paste the names, so no need to do so,  just Prof. or Dr. Lastname.

@@

\begin{commentbox}[Vu]
    I've been called Dr. Vu and I find it a bit amusing but am totally fine with it.
\end{commentbox}

@@

%\subsection{Having fun during a PhD?}
%PhD students \emph{and faculty} probably find it amusing about the notion that students, especially international ones, can genuinely enjoy their PhD studies. In fact, after reading posts after posts on VietPhD.org on how PhD students are commonly mistreated, stressed, it seems being miserable is a norm during a PhD study.

%There are many advice on surviving PhD that you can follow. But here I just list a few that works for me and what I advice my students to do.\tvn{TODO}
